---
title: "Module 9 Notes"
output: html_document
date: "2024-01-31"
---
## 5-number Summary

## Module 9 Exercises
```{r}
library(tidyverse)
f <- "https://raw.githubusercontent.com/difiore/ada-2024-datasets/main/Country-Data-2016.csv"
d <- read_csv(f, col_names = TRUE)
names(d)
attach(d)
plants
```

### Challenges

```{r}
library(tidyverse)
f <- "https://raw.githubusercontent.com/difiore/ada-2024-datasets/main/Country-Data-2016.csv"
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
d <- as_tibble(d)
```
```{r}
head(d)
```
```{r}
names(d)
```
```{r}
summary(d)
```
**How many variables?**
16

**How many observations?**
248
```{r}
c <- length(unique(d$country))
```
**How many countries?**
248

```{r}
median(d$area, na.rm = TRUE)
```
**Median area?**
69700

```{r}
median(d$population, na.rm = TRUE)
```
**Median population size?**
4911766

**Create new density variable (population/area) in the data frame**
```{r}
d$density <- d$population/d$area
```

**What are the 10 most dense countries?**
```{r}
d <- d |> arrange(desc(density))
head(d,10)
```
**What are the 10 least dense countries?**
```{r}
d <- d |> arrange(desc(density))
tail(d,10)
```
## For Monday: 
### Read rest of Module 9 and Module 10
### Be prepared to work through Exercise 3 in class